How to compute the fusion product of MV cycles in type A

### 2021-05-05 draft.tex
we havent defined G1

\begin{definition}
\label{def:klslice}
    The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
\end{definition}
%

@@

Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. 
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
\end{corollary}
The irreducible components of the closure of the intersection on the lefthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By BKK the set of MV cycles of all possible types and weights can be glued together to form a \textbf{perfect basis} of $\CC[N]$.

@@

\section{Falling Action} % Resolution
\subsection{MV cycles}
\begin{itemize}
    \item $\overline{A(n_\bullet)}$
    \item $D_\gamma$ 
    \item MV basis?
\end{itemize}
% \acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis. Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with. This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
% 
\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu' +\mu''$, and $\lambda =\lambda'+\lambda''$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda',\lambda''}\cap\TT_{\mu',\mu''} \to \overline\Gr_\AA^{\lambda',\lambda''}\cap \cW_{\mu',\mu''}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda',\lambda''}^s}\cap\TT_{\mu',\mu''}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu'} (t-s)^{\mu''} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

Let's call this the MVyBD isomorphism.

\begin{proof}
    The proof is fibre by fibre, so fix $s\ne 0$. \acom{Emphasize in the intro later (because this always confuses me) that by the $s$-fibre we really mean the $(0,s)$-fibre; i.e.\ its the BD Grassmannian over the second symmetric power of $C = \AA^1$; better just replace $s$-fibre by $(0,s)$-fibre everywhere it occurs.}
    \begin{enumerate}
        \item The map is well defined. In particular, it defines $\CC[t]$-lattices in $\CC(t)^m$. Moreover, these lattices break down to give pairs of lattices upon inverting $t$ or $t-s$ that have the right properties. [Copy Roger's proof]
        \item The inverse map is got by taking the matrix of multiplication by $t$.  More precisely, let $ L \in Gr^{BD} \cap \cW_\mu$.  We work with the quotient $\CC[t]^m/L$ just as in the ordinary MVy isomorphism---the only difference being $\CC\xt$ is replaced by $\CC[t]$.
\begin{enumerate}
    \item 
    We claim that 
    \begin{equation}
        \{[e_i],[te_i],\dots,[t^{\mu_{i}-1}e_i] : 1\le i \le m\}
    \end{equation}
    is a $\CC$-basis of $\CC[t]^m/L$.

    To see this, we use that $ L $ 
 has a $\CC[t]$-basis of the form 
    \begin{equation}
        v_i = t^{\mu_i} + \sum_{j>i} p_{ij}(t) e_j 
    \end{equation}
    with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu',\mu''}$ in this way?}
    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda'$ while its generalized $s$-eigenspace will have block type $\le \lambda''$. 
    To see this, note that there is a natural isomorphism
    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
    carrying the action of $t $ to the action of $t$.

    The left hand side is the same thing as
    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$

    the defining fact that lattices satisfying Equation~\ref{eq:defGrBDlambda} equivalently satisfy 
    \begin{equation}
        \begin{split}
            t\big|_{\CC\xt^m/L_1}\text{ has Jordan type} \le \lambda' \\
            t\big|_{\CC\xt^m/L_2}\text{ has Jordan type} \le \lambda'' 
        \end{split}
    \end{equation}
    where recall 
    $L_i = L\otimes \CC\xt$ ??? 
    % $L_i = L\otimes \CC[(t-p_i)^{-1}]$ 
    and $p_1 = s$ while $p_2 = 0$.

    $$\CC\xt^m/(L \otimes_{\CC[t]} \CC\xt) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
    carrying the action of $t $ to the action of $t$.

    The left hand side is the same thing as
    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
    \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
\end{enumerate}
    \end{enumerate}
\end{proof}

\begin{theorem}[Theorem 1 version 2]
    Let $\lambda_1,\lambda_2$ and $\mu$ 
    %be dominant
    be arbitrary, such that $\lambda = \lambda_1 + \lambda_2 \ge \mu$. Then there is an isomorphism 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}} \cap \TT_\mu \to \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu 
    \end{equation}
    defined by the same map as in Theorem 1.
\end{theorem}

\jcom{This is true as stated with the ``larger'' definition of $ \cW_\mu $.  In fact, for any $\lambda_1, \lambda_2$, it is true $ \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu $ is contained in a subset that we could call $ \cW_\mu^s$ which we could define as
$$
\cW_\mu^s = G_1\xt[t^{-1}]\TT_\mu \cap G[t,t^{-1}, (t-s)^{-1}] / G[t]
$$
where we regard $G[t,t^{-1}, (t-s)^{-1}] / G[t] \subset G\xT[t^{-1}]/G[t] $

The way to think about this is as follows: inside the thick affine Grassmannian we can consider the $G$-bundles trivialized away from just 0, $s$, or equivalently those lattices which become the standard lattice after tensoring with $ \CC[[t-a]] $ for any $ a \ne 0, s$.
}
\begin{corollary}
    The MVyBD isomorphism restricts to an isomorphism of subfamilies 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+ \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu''}\,. 
    \end{equation}
\end{corollary}

\begin{proof}
    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovi\'c-Vybornov isomorphism.  Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
    So we get containment in one direction.

    For the reverse containment, we choose $ [g] \in \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu',\mu''}$.  By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
\end{proof}

% Define $S_{\mu',\mu''}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

\acom{is it a fibre of $S_{\mu',\mu''}$ defined above?}

We could also make the following claim.

\begin{lemma}[KWWY14]
    Let $\mu$ be dominant. Then 
    \begin{equation}
        N_{-}\xT[t^{-1}] L_\mu = N_1\xt[t^{-1}]L_\mu
    \end{equation}
    \acom{where I am not sure about the double brackets.}
\end{lemma}

\begin{lemma}%[Roger's lemma]
    Let $\mu',\mu''$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu',\mu''}^s \subset \cW_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1\xt[t^{-1}].
\]
\end{proof}
\end{comment}
% 
\subsection{Alternate MV}
We begin this section with some new notation. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of (arbitrary) shape $\lambda$ and (arbitrary) weight $\mu$. Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
% For the sake of making a definition, we momentarily put some letters of our alphabet in unexpected roles, and ask you to suspend your disbelief. Given an arbitrary tableau $t$ having weight $w$ and shape $s$, we denote by $s(i)$ (resp.\ $w(i)$) the shape (resp.\ the weight) of $t(i)$, the tableau got from $t$ by discarding all boxes of weight exceeding $i$.

Given $\tau\in YT(\lambda)_\mu$ denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$. 
%

The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is got from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
$$
n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
$$
for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
% 
For example, if 
\[
    \tau = \young(1112,23) 
\]
then
\begin{gather*}
%    \text{if } \tau = \young(1112,23) \text{ then } 
\gt(\tau) = \begin{matrix}
       3 \\
       4 & 1 \\ 
       4 & 2 & 0 
   \end{matrix} \text{ and }
   n_\bullet(\tau) = (1,0,1)\,. 
\end{gather*}
% 
This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
% 
We can associate to $\tau$ an MV cycle. \acom{which is something we haven't introduced yet.} Let 
%  
\begin{equation*}
    Z(\tau) = 
    % \overline{
        \{
            L\in S^\mu : L\cap\CC[t]^i\in\Gr^{\lambda(i)}\text{ for all }i 
        \}\,. 
    % }
\end{equation*}
% 
\begin{proposition}
    \label{pr:newmvdes}
    $\overline{Z(\tau)}$ the MV cycle whose Lusztig datum is $n_\bullet(\tau)$. 
\end{proposition}
% This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all 
% % but its first $i$ boxes
% boxes of weight exceeding $i$. 
% % If the tableau contains repeated entries then first means leftmost.
% 
% \jcom{I don't think that you should mention this partial inverse here.  I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
% \acom{Ok, I moved it.}

@@

\begin{conjecture}
    The cluster monomials of $\CC[N]$ are elements of the MV basis.
\end{conjecture}

It has been shown in \cite{kato2011polytopal} that for certain initial seeds $(x_1, \dots, x_r)$, each $x_i$ is in the MV basis. Then to show every cluster variable is in the MV basis, it suffices to show that for a mutable variable $x_i$, its mutation $x_i^*$ is also in the MV basis. The exchange relation corresponding to $x_i$ and $x_i^*$ is of the form
$$x_ix_i^* = x_+ + x_-$$
where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$. Let $Z_i$, $Z_+$, and $Z_-$ be the corresponding MV cycles for $x_i$, $x_+$, and $x_-$, respectively. If we are able to find an MV cycle $Z_i^*$ such that
$$Z_i \circ Z_i^* = Z_+ \cup Z_-,$$
then this means $x_i^*$ is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$. 
\section{Denouement}
\label{s:denouement}
\subsection{Examples}

>>>>

\begin{definition}
\label{def:klslice}
    The \textbf{Kazhdan--Lusztig slice} $\cW_\mu = G_1(\Oinf) t^\mu \subset \Grth $.  
\end{definition}
% 
\acom{we haven't defined $G_1$}

@@

Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. 
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
\end{corollary}
The irreducible components of the closure of the intersection on the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By BKK the set of MV cycles of all possible types and weights can be glued together to form a \textbf{perfect basis} of $\CC[N]$.

@@

\section{Falling Action} % Resolution
\subsection{MV cycles}
\begin{definition}
An irreducible component of $ \overline{\Gr}^\lambda \cap S^\mu $ is called an \textbf{Mirkovic-Vilonen cycle} in $ \overline{\Gr}^\lambda$ of coweight $\mu$.
\end{definition}

\jcom{We could put some stuff here about stable MV cycles and multiplication, but maybe we can have this in a later section.}

% \acom{Recall (from optional \Cref{s:exposition}) the question motivating this work --- Roger's thesis, cluster monomials and the MV basis. Clarify that whereas we have so far only seen spaces related to ``ordinary MV cycles'' it is the ``stable MV cycles'' that are used to define the MV basis of $\CC[N]$ that the motivating question is concerned with. This discrepancy is the reason we might want to discuss maps $B(\infty)\to B(\lambda)$.}
%

In \cite{mvcycle}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic-Vilonen polytopes, or equivalently Lusztig data.  For $ GL_m$, this description can be reworded in terms of Young tableaux. 
\jcom{Maybe add something here about Lusztig data and the standard reduced word.}

We begin with some new notation. Let $YT(\lambda)_\mu$ denote the set of (possibly semistandard) Young tableaux of shape $\lambda$ and weight $\mu$. 
%Here, the weight of a tableau is a sequence $(\mu_1,\mu_2,\dots)$ recording the number of boxes of weight $i = 1,2,\dots$ that the tableau contains, and the weight of a box is just the number that the box contains.
% For the sake of making a definition, we momentarily put some letters of our alphabet in unexpected roles, and ask you to suspend your disbelief. Given an arbitrary tableau $t$ having weight $w$ and shape $s$, we denote by $s(i)$ (resp.\ $w(i)$) the shape (resp.\ the weight) of $t(i)$, the tableau got from $t$ by discarding all boxes of weight exceeding $i$.

Given $\tau\in YT(\lambda)_\mu$ and $ i \in \{1, \dots m\} $, denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$. (Note that $ \mu(i)$ only depends on $ \mu$, while $ \lambda(i)$ depends on the tableau $ \tau$.)  We will regard $ \lambda(i)$ (resp. $\mu(i)$) as an effective dominant coweight (resp. effective coweight) for $GL_i$. 
%

The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
$$
n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
$$
for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}

For example, if 
\[
    \tau = \young(1112,23) 
\]
then
\begin{gather*}
%    \text{if } \tau = \young(1112,23) \text{ then } 
\gt(\tau) = \begin{matrix}
       3 \\
       4 & 1 \\ 
       4 & 2 & 0 
   \end{matrix} \text{ and }
   n_\bullet(\tau) = (1,0,1)\,. 
\end{gather*}
% 
%This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
% 
We can associate to $\tau$ an MV cycle. \acom{which is something we haven't introduced yet.} Let 
%  
\begin{equation*}
    Z(\tau) = 
     \overline{
        \{
            L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
        \}\,. 
     }
\end{equation*}
%

The following result is closely related to Theorem 4 from \cite{dranowski2020generalized}.  It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson-Kogan \cite{andersonkogan1} (see Section 9 in \cite{mvcycle}).  We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent-Littelmann-Nguyen \cite[Theorem 2]{GLN}.
\begin{proposition}
    \label{pr:newmvdes}
    $Z(\tau)$ the MV cycle whose Lusztig datum with respect to $ \vi $ is $n_\bullet(\tau)$. 
\end{proposition}
\begin{proof}
    The proof of this theorem follows the same strategy as in \cite{dranowski2020generalized}.
\jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}

Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.

\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}

First, we consider
\begin{equation*}
Z(\tau)_1 := \{ L \in S^\mu : L \cap \cO^i \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
\end{equation*}
From Corollary 9.7 of \cite{mvcycle}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{mvcycle}.  Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.  We also note that $Z(\tau_1) \subset \Gr^\lambda$ is dense in $ Z(\tau_1)$.  
\jcom{Need to justify this last sentence.}

Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu$, then $ L \cap \cO^i \in S^{\mu(i)}$.  Thus, we get a map $$ f_i : Z(\tau)_1 \rightarrow S^{\mu(i)} \cap S_+^{\lambda(i)} $$
From the definition of $ Z(\tau)_1 $, we see that $ f_i(Z(\tau_1) = Z(\tau(i)_1)$.  From above $ \Gr^{\lambda(i)} \cap f_i(Z(\tau(i)_1))$ is a dense constructible subset of $Z(\tau(i)_1)$.  Since $ Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ is a dense constructible subset of $ Z(\tau_1) $.

Working with all $ i $ at once, we conclude that
$$ Z(\tau)_2 := \bigcap_{i=1}^m f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $$
is a dense constructible subset of $ Z(\tau)_1$.  Thus $\overline{Z(\tau)_2} = \overline{Z(\tau)_1}$.

On the other hand, by definition 
$$Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}$$

\jcom{Now, we need to show density here.  But maybe that won't be possible and we will need to take the ``top''.}

    %See computation 5.3.9 and Lemma 5.4.2 (ignore its proof) of \url{http://www.math.toronto.edu/adranows/athesis.pdf}. 
\end{proof}
% This gives us the dimension of Gr^\lambda \cap Gr_\mu \cap S^\mu.
% Given $(\tau',\tau'')\in YT(\lambda')_{\mu'}\times YT(\lambda'')_{\mu''}$ denote by $\lambda'(i),\lambda''(i)$ (resp.\ $\mu'(i),\mu''(i)$) the shape (resp.\ the weight) of $\tau'(i),\tau''(i)$ where $\tau^?(i)$ denotes the tableau got from $\tau^?$ by discarding all 
% % but its first $i$ boxes
% boxes of weight exceeding $i$. 
% % If the tableau contains repeated entries then first means leftmost.
% 
% \jcom{I don't think that you should mention this partial inverse here.  I think that you should explain here how the generalized orbital varieties are indexed by the tableaux, in other words, how $ X(\tau) $ is defined.}
% \acom{Ok, I moved it.}

@@

\begin{conjecture}\label{conj:cluster in MV}
    The cluster monomials of $\CC[N]$ are elements of the MV basis.
\end{conjecture}

Conjecture \ref{conj:cluster in MV} is known for type $A_n$, $n \leq 3$, as in this case, there is a unique biperfect basis for $\CC[N]$ \cite{baumann2019mirkovic}, so the dual semicanonical basis and MV basis are the same.

It has been shown in \cite{kato2011polytopal} that for initial seeds $(x_1, \dots, x_r)$ obtained from a reduced expression of the longest word in the Weyl group for $G$, each $x_i$ is in the MV basis as these correspond to generalized minors \cite{berenstein2005cluster3}\cite{geiss2007initial}. If the reduced expression satisfies a special condition, then the cluster monomials in the initial seed are also in the MV basis \cite{baumann2020bases}.

Suppose we have a seed $(x_1, \dots, x_r)$ where each $x_i$ is already in the MV basis. To show all the other cluster variables are in the MV basis, it suffices to show that for a mutable variable $x_i$, its mutation $x_i^*$ is also in the MV basis. The exchange relation corresponding to $x_i$ and $x_i^*$ is of the form
$$x_ix_i^* = x_+ + x_-$$
where $x_+$ and $x_-$ are monomials in the $x_j,j\neq i$. Let $Z_i$ be the MV cycle corresponding to $x_i$, so $x_i = b_{Z_i}$. If we are able to find an MV cycle $Z_i^*$ such that
$$b_{Z_i} b_{Z_i^*} = x_+ + x_-,$$
then this means $x_i^* = b_{Z_i^*}$ so it is in the MV basis with associated MV cycle $Z_i^*$. In Section \ref{s:denouement}, we present examples showcasing this is indeed true for type $A_3$. 
\section{Denouement}
\label{s:denouement}
\subsection{Examples}
